Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-23 WSSSPE2_report/WSSSPE2_review.tex
Section 3: tiny changes.
Section 7: minor changes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes\todo{\footnotesize{Lead: Choi. \href{http://tinyurl.com/q6ew45v}{Google Notes} and \href{http://tinyurl.com/pd9tmh3}{here}}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
\href{http://tinyurl.com/mnenzms}{Abstracts}.  \href{http://tinyurl.com/las8tsq}{Slides}.}
} \label{sec:keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The workshop featured two keynote addresses. In the opening keynote
presentation, Kaitlin Thaney of the Mozilla Science Lab talked about her
organization's work and policy to enable and support sustainable and
reproducible scientific research through the open web. The second keynote
speaker was Neil Chue Hong of Software Sustainability Institute. He shined a
light on how scientific software is prevalently driving advances in many science
and engineering fields. Both keynote speeches spawned further discussion among
workshop participants on the crucial notion ``sustainability'' in the theme of
our workshop.

@@

Prizes in different categories were discussed (like Academy Awards), for example:
best contribution (non-founder),
broadest diversity of contributions,
best tutorials/documentation,
best leadership transition (award ex leader and new leader),
best generalization (taking something that was limited and making it more general), and
best mentorship of contributors (bringing others into the community).

\katznote{I don't understand this at all.  Can some explain it?}
There are also other indirect forms of incentives
(though these are not a direct prize, they still can incentivize someone):
\begin{itemize}
\item Converting reputation by joining apache software foundation, Google etc. 
\item Inviting ASF and open source people to contribute to scientific code (at
least on questions of overlapping
\item Template for assessing scientific contributions made through software.   
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Keynotes\note{\footnotesize{Lead: Choi. \href{http://tinyurl.com/q6ew45v}{Google Notes} and \href{http://tinyurl.com/pd9tmh3}{here}}.
%https://docs.google.com/document/d/1-BxkYWDQ6nNNBXBStUL0xcKF9qCTlEALwf928J_MemI/edit?usp=sharing
\href{http://tinyurl.com/mnenzms}{Abstracts}.  \href{http://tinyurl.com/las8tsq}{Slides}.}
} \label{sec:keynotes}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The workshop featured two keynote addresses. In the opening keynote
presentation, Kaitlin Thaney of the Mozilla Science Lab talked about her
organization's work and policy to enable and support sustainable and
reproducible scientific research through the open web. The second keynote
speaker was Neil Chue Hong of Software Sustainability Institute. He shined a
light on how scientific software is prevalently driving advances in many science
and engineering fields. Both keynote speeches spawned further discussion among
workshop participants on the crucial notion \emph{sustainability} in the theme of
our workshop.

@@

Prizes in different categories were discussed (like Academy Awards), for example:
best contribution (non-founder),
broadest diversity of contributions,
best tutorials or documentation,
best leadership transition (award ex leader and new leader),
best generalization (taking something that was limited and making it more general), and
best mentorship of contributors (bringing others into the community).

\katznote{I don't understand this at all.  Can someone explain it?}
There are also other indirect forms of incentives
(though these are not a direct prize, they still can incentivize someone):
\begin{itemize}
\item Converting reputation by joining the Apache Software Foundation, Google, etc. 
\item Inviting ASF and open source people to contribute to scientific code (at
least on questions of overlapping
\item Template for assessing scientific contributions made through software.   
\end{itemize}
